Analyzing the Relationship between Increased Employment Rates and Higher Permanent Immigrant Inflows

### 2023-04-19 outputs/paper/paper.qmd
citation change

In this paper, we will examine the relationship between Canada's employment rate and permanent immigrant inflows through a linear regression analysis. The estimand here is how employment rate and immigrants inflows are related. Specifically, we will focus on Canada, which has a relatively high immigration number. We will draw data from the OECD website [@cite]. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development. This exploration can provide valuable insights for government oﬀicials and policy makers in developing policies to attract and retain permanent immigrants and influencing permanent immigrant inflows. In addition, this research can impact economic development strategies which can benefit the labour market and immigration.

@@

The data used in this paper is obtained from the OECD Data (Organisation for Economic Co-operation and Development) and is publicly available through the OECD website [@OECD]. Founded in 1961, the OECD is an intergovernmental organisation with 38 member countries collaborating to develop policy standards to promote sustainable economic growth. The organization's data is widely used by policymakers, researchers, and analysts to understand trends and inform policy decisions. The OECD has collected data regarding economy, education, employment, environment, health, tax, trade, GDP, unemployment rate, and inflation. It keeps records on a monthly, quarterly, and yearly data from the participating countries.

@@

The three datasets that I will be using are: Permanent immigrant inflows [@OECDPermanent], Employment Rate [@OECD2023], and Population [@OECDPopulation]. All of them will be specifically Canada and have evolved from 2009 to 2019. Permanent immigrant inflows cover regulated movements of foreigners considered to be settling in the country from the perspective of the destination country. The data presented are the result of a standardization process in Canada. The number of variables recorded in the data was 253 101 in 2009, 262 773 in 2013, and 341 173 in 2019. Employment rates are a measure of the extent to which available labour resources (people available to work) are being used. They are calculated as the ratio of the employed to the working age population. The working age population refers to people aged 15 to 64. The percentage of variables recorded in the data was 71.5 in 2009, 2.7 in 2013, and 74.6 in 2019. Finally, the population is defined as all nationals present in, or temporarily absent from a country, and aliens permanently settled in a country. This indicator shows the number of people that usually live in an area. Growth rates are the annual changes in population resulting from births, deaths, and net migration during the year.

@@

Our paper analyzes the relationship between employment rate and permanent immigrant inflows. However, our data only examines the employment rate over the last decade and is insufficient to support the analysis. Therefore, we could expand on the dataset over the last 50 years and can help to better understand how the relationship between employment rate and permanent immigrant inflows has evolved over time in Canada. This can also help to identify any long-term trends or patterns that may not be apparent. To further strengthen our findings, we can incorporate other data sources from other countries with high immigrants such as the USA, UK, and Australia, and compare the data to identify any commonalities or differences in the relationship between employment rate and permanent immigrant inflows across different contexts. Moreover, we can look at additional variables such as wage data to develop a multi-linear regression model to capture the other factors that can influence the relationship between employment rate and permanent immigrant inflows. Finally, we need to consider the potential confounding variables such as the overall state of the Canadian economy when analyzing the relationship between employment rate and permanent immigrant inflows. If the Canadian economy is performing well and experiencing a period of growth, it may lead to both an increase in the employment rate and an increase in permanent immigrant inflows.

>>>>

In this paper, we will examine the relationship between Canada's employment rate and permanent immigrant inflows through a linear regression analysis. The estimand here is how employment rate and immigrants inflows are related. Specifically, we will focus on Canada, which has a relatively high immigration number. We will draw data from the OECD website [@OECD]. Our respondents of interest are the percentage of the working-age population, as they represent the potential labor force and have a significant impact on a country's economic growth and development. This exploration can provide valuable insights for government oﬀicials and policy makers in developing policies to attract and retain permanent immigrants and influencing permanent immigrant inflows. In addition, this research can impact economic development strategies which can benefit the labour market and immigration.

@@

The data used in this paper is obtained from the OECD Data (Organization for Economic Co-operation and Development) and is publicly available through the OECD website [@OECD]. Founded in 1961, the OECD is an intergovernmental organisation with 38 member countries collaborating to develop policy standards to promote sustainable economic growth. The organization's data is widely used by policymakers, researchers, and analysts to understand trends and inform policy decisions. The OECD has collected data regarding economy, education, employment, environment, health, tax, trade, GDP, unemployment rate, and inflation. It keeps records on a monthly, quarterly, and yearly data from the participating countries.

@@

The three datasets that I will be using are: Permanent immigrant inflows [@OECDPermanent], Employment Rate [@OECDemployment], and Population [@OECDPopulation]. All of them will be specifically Canada and have evolved from 2009 to 2019. Permanent immigrant inflows cover regulated movements of foreigners considered to be settling in the country from the perspective of the destination country. The data presented are the result of a standardization process in Canada. The number of variables recorded in the data was 253 101 in 2009, 262 773 in 2013, and 341 173 in 2019. Employment rates are a measure of the extent to which available labour resources (people available to work) are being used. They are calculated as the ratio of the employed to the working age population. The working age population refers to people aged 15 to 64. The percentage of variables recorded in the data was 71.5 in 2009, 2.7 in 2013, and 74.6 in 2019. Finally, the population is defined as all nationals present in, or temporarily absent from a country, and aliens permanently settled in a country. This indicator shows the number of people that usually live in an area. Growth rates are the annual changes in population resulting from births, deaths, and net migration during the year.

@@

Our paper analyzed the relationship between employment rate and permanent immigrant inflows. However, our data only examines the employment rate over the last decade and is insufficient to support the analysis. Therefore, we could expand on the dataset over the last 50 years and can help to better understand how the relationship between employment rate and permanent immigrant inflows has evolved over time in Canada. This can also help to identify any long-term trends or patterns that may not be apparent. To further strengthen our findings, we can incorporate other data sources from other countries with high immigrants such as the USA, UK, and Australia, and compare the data to identify any commonalities or differences in the relationship between employment rate and permanent immigrant inflows across different contexts. Moreover, we can look at additional variables such as wage data to develop a multi-linear regression model to capture the other factors that can influence the relationship between employment rate and permanent immigrant inflows. Finally, we need to consider the potential confounding variables such as the overall state of the Canadian economy when analyzing the relationship between employment rate and permanent immigrant inflows. If the Canadian economy is performing well and experiencing a period of growth, it may lead to both an increase in the employment rate and an increase in permanent immigrant inflows.
